Demes: a specification for interchanging complex demography

### 2021-06-18 paper.tex
Apply suggestions from code review
Co-authored-by: Graham Gower <graham.gower@gmail.com>

Stable and healthy software ecosystems require standard interchange
formats, allowing for the development of high-quality and long-lasting
tools that produce and consume the standard.
Demographic models are a key part of population genetics research,
and to date the transfer of inferred models to downstream simulations
has been ad-hoc, and conversions between the many different ways
of expressing such models both labour intensive and fraught with errors.
The proposed Demes standard is an attempt to bridge this gap
between inference and simulation, and also to provide the foundations
for a sustainable ecosystem of tools built around this data model.
Table~\ref{tab-software} shows some initial infrastructure that we have
built as part of developing Demes, but many other useful tools
can be envisaged that either produce or consume this format.

% Could finish up here by talking about reproducibility?

>>>>

Stable and healthy software ecosystems require standard interchange
formats, allowing for the development of high-quality and long-lasting
tools that produce and consume the standard.
Demographic models are a key part of population genetics research,
and to date the transfer of inferred models to downstream simulations
has been ad-hoc, and conversions between the many different ways
of expressing such models is both labour intensive and fraught with errors.
The proposed Demes standard is an attempt to bridge this gap
between inference and simulation, and also to provide the foundations
for a sustainable ecosystem of tools built around this data model.
Table~\ref{tab-software} shows some initial infrastructure that we have
built as part of developing Demes, but many other useful tools
can be envisaged that either produce or consume this format.

A standard format also serves to improve scientific reproducibility. Authors simply include their demographic model as a supplementary file, or upload it to a data repository, so that readers need not transcribe the model themselves. This removes the opportunity for error due to model misinterpretation or incorrect translation to a simulatable format. In the event that the Demes standard becomes outdated, published Demes files will be convertible to future formats with relative ease because the data model is unambiguously specified.
